Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2018-01-21 writeup/response2reviews.tex

\item Second, the simulation scenario should correspond to a real biological scenario. Here this layer-based simulation scenario is very difficult to understand. I would be more interesting to stick to more classic spatially explicit simulations such as range expansion, or secondary contact scenarios.\\\\
\gb{We appreciate that the simulation scenario we ran is somewhat artificial, 
and that it would be good to test the behavior of the method 
under a classic ``isolation followed by expansion into a zone of secondary contact" model.
However, as we discuss in the manuscript in the section ``Simulation details",
we wanted to simulate datasets that had unambiguous true admixture proportions, 
so that we could test \texttt{conStruct}'s ability to estimate admixture accurately 
(shown in SuppMat figures XXX and XXX).
A more organic simulation, with isolation followed by expansion, 
secondary contact, and subsequent admixture, 
would not facilitate that test in a straightforward way. 
As mentioned by Reviewer 2, there are an enormous number 
of possible simulations we could run to test \texttt{conStruct}'s performance, 
but fully exploring them is beyond of the scope of this manuscript, 
so we intend to pursue those in future work.}\\

\item Third, I think that the main point of the paper should be more explicit. Non-spatial model based approaches are prone to overfitting when K is too large and this can be avoided when using spatial-based approaches. \\\\
Good suggestion; we've added a line to the Abstract to this effect.\\

@@

\item 100: Is there a reason that allelic covariance is used instead of genetic covariance?\\\\
\gb{
    Good question; we've added some more text for this, 
    both explaining what the allelic covariance is and why we use it in lieu of the genetic covariance,
    (Lines XXX-XXX).
    The short answer is that the allelic covariance is insensitive to the choice of reference allele, 
    and, because it doesn't subtract off means like the genetic covariance, 
    has a constant value between a pair of samples in the dataset, 
    regardless of which other samples are included.
}\\

\item Could supp. figures be sorted according to first mentioning in ms?\\\\
\gb{MAKE SURE THIS IS RIGHT AFTER MAKING SUBMISSION MS}\\

\item Fig3: increase label size\\\\
\gb{Fixed.}\\

\item Last line in paragraph on p. 18: as the derivations are otherwise very detailed and easy to follow, it might be worth adding here that this follows from E[UV] = 4 Cov[A, B]\\\\
We have substantially rewritten tihs section.  \\

### 2018-01-21 writeup/conStruct.tex
tweaks about responses

A classic problem in population genetics is the characterization 
of discrete population structure in the presence of 
continuous patterns of genetic differentiation.
Especially when sampling is discontinuous, 
the use of clustering or assignment methods may incorrectly ascribe
differentiation due to continuous processes (e.g., geographic isolation by distance)
to discrete processes, such as geographic, ecological, or reproductive barriers 
between populations.
This reflects a shortcoming of current methods for inferring and 
visualizing population structure when applied to genetic data
deriving from geographically distributed populations.
Here, we present a statistical framework for the simultaneous inference 
of continuous and discrete patterns of population structure.
The method estimates ancestry proportions for each 
sample from a set of two-dimensional population layers, 
and, within each layer, estimates a rate at which relatedness decays with distance.
This thereby explicitly addresses the ``clines versus clusters" problem in 
modeling population genetic variation.
The method produces useful descriptions of structure in genetic relatedness
in situations where separated, geographically distributed populations interact,
as after a range expansion or secondary contact.
We demonstrate the utility of this approach using simulations 
and by applying it to empirical datasets of poplars and black bears in North America.

>>>>

A classic problem in population genetics is the characterization 
of discrete population structure in the presence of 
continuous patterns of genetic differentiation.
Especially when sampling is discontinuous, 
the use of clustering or assignment methods may incorrectly ascribe
differentiation due to continuous processes (e.g., geographic isolation by distance)
to discrete processes, such as geographic, ecological, or reproductive barriers 
between populations.
This reflects a shortcoming of current methods for inferring and 
visualizing population structure when applied to genetic data
deriving from geographically distributed populations.
Here, we present a statistical framework for the simultaneous inference 
of continuous and discrete patterns of population structure.
The method estimates ancestry proportions for each 
sample from a set of two-dimensional population layers, 
and, within each layer, estimates a rate at which relatedness decays with distance.
This thereby explicitly addresses the ``clines versus clusters" problem in 
modeling population genetic variation,
and avoids problems with overfitting that nonspatial models are prone to.
The method produces useful descriptions of structure in genetic relatedness
in situations where separated, geographically distributed populations interact,
as after a range expansion or secondary contact.
We demonstrate the utility of this approach using simulations 
and by applying it to empirical datasets of poplars and black bears in North America.
